### 2022-07-15 ms/ms.rmd
Priors
Adding some questions to guide us again

### *Meta-Analysis*
We analysed our data using Bayesian multilevel meta-analytic and meta-regression models in R (vers. `r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers. `r utils::packageVersion("brms")` @Burkner2018; @Burkner2017; @stan]. 
@Guangchuang2017

@@

## Results

>>>>

### *Meta-Analysis*
We analysed our data using Bayesian multilevel meta-analytic and meta-regression models in R (vers. `r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers. `r utils::packageVersion("brms")` @Burkner2018; @Burkner2017; @stan]. We included study, species and phylogeny as random effects to account for non-independence and also explore drivers of variation among $lnRR_{Q_{10}}$ estimates.

@Guangchuang2017

@@

## *Results*

### *Do terrestrial and aquatic ectotherms differ in their capacity to acclimate?*
### *Does climate variability predict acclimation capacity among aquatic and terrestrial ectotherms?*
### *Does between-individual variation in acclimation capacities differ across terrestrial and aquatic ectotherms?*
